---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dePlzMap

<!-- badges: start -->
<!-- badges: end -->

The `dePlzMap` R package is a tool for visualizing data on a map of Germany, 
using postal code (PLZ) boundaries as geographic units. 
It provides a simple and flexible interface for creating [choropleth maps](https://en.wikipedia.org/wiki/Choropleth_map) of 
PLZ regions in Germany with continuous color scales,
allowing users to explore spatial patterns and relationships in data.
The package includes the possibility to normalize the input values by population
per PLZ region to show population-relative values.
The package leverages the `ggplot2` and `ggmap` libraries for generating the plots.
The plots can be created via the function `dePlzMap` which users can quickly generate 
informative maps that highlight patterns in via R.

## Data

The population data is based on the data from the ["Registerzensus 2011"](https://www.zensus2011.de/DE/Home/Aktuelles/DemografischeGrunddaten.html?nn=559100) of the 
Statistisches Bundesamt in Deutschland and was obtained from the web site [https://www.suche-postleitzahl.org](https://www.suche-postleitzahl.org/downloads).

The shape files that describe the borders of the PLZ regions have also been 
drawn from [https://www.suche-postleitzahl.org](https://www.suche-postleitzahl.org/downloads).

The shape data for the borders of the German states is from https://public.opendatasoft.com/.

## Licensing

The geographic data used by the package 
is derived from [OpenStreetMap](https://www.openstreetmap.org/) and uses the 
[Open Database License](https://opendatacommons.org/licenses/odbl/)
(&copy; OpenStreetMap contributors).

The population data is copyrighted by Statistisches Bundesamt 2014, which
allows the distribution, also in parts, if the source is specified.

Apart from the data, the package is licensed under the MIT license (&copy; Stefan Lenz 2023).

## Installation

You can install the `dePlzMap` package from [GitHub](https://github.com/) in R via:

``` r
# install.packages("devtools")
devtools::install_github("stefan-m-lenz/dePlzMap")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dePlzMap)
## basic example code
```


You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
